Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-04 ms.tex
trying to fix up presentation of chi-squared equation
clarifying notation for single-MBB case

\begin{deluxetable*}{llrrrrrrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{11} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Number} &
\colhead{Model} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$} &
\colhead{$T_2$} &
\colhead{$T_1$} &
\colhead{$n$} &
\colhead{D.O.F.} &
\colhead{$\chi^2$} &
\colhead{$\chi^2_{\nu}$}
}
\startdata
 1 & FDS99 best-fit  & 0.0363 & 13.0  & 1.67 & 2.70 & 15.72 &  9.15 & 1.018 & 7 & 23.9 & 3.41 \\
 2 & FDS99 general   & 0.0485 & 8.22  & 1.63 & 2.82 & 15.70 &  9.75 & 0.980 & 3 & 3.99 & 1.33 \\
 3 & single MBB      &  1.0   &  ...  & 1.59 &  ... &  ...  & 19.63 & 0.999 & 6 & 33.9 & 5.65 \\ [-2ex]
\enddata
\end{deluxetable*}

@@

We assume an uncertainty of 2\% on each of the 9 correlation slopes and
minimize the $\chi^2$ given by:

@@

\begin{equation}
\chi^2 = \sum_{i=0}^{8}\frac{(s_{i, 857}-n\tilde{I}_{\nu_i}/\tilde{I}_{857})^2}{\sigma_{s}^2}
\end{equation}

>>>>

\begin{deluxetable*}{llrrrrrrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{11} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Number} &
\colhead{Model} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$} &
\colhead{$T_2$} &
\colhead{$T_1$} &
\colhead{$n$} &
\colhead{D.O.F.} &
\colhead{$\chi^2$} &
\colhead{$\chi^2_{\nu}$}
}
\startdata
 1 & FDS99 best-fit  & 0.0363 & 13.0  & 1.67 & 2.70 & 15.72 &  9.15 & 1.018 & 7 & 23.9 & 3.41 \\
 2 & FDS99 general   & 0.0485 & 8.22  & 1.63 & 2.82 & 15.70 &  9.75 & 0.980 & 3 & 3.99 & 1.33 \\
 3 & single MBB      &  0.0   &  ...  &  ... & 1.59 & 19.63 &   ... & 0.999 & 6 & 33.9 & 5.65 \\ [-2ex]
\enddata
\end{deluxetable*}

@@

We assume an uncertainty of 2\% on each of the $s_{i, 857}$ and minimize the 
chi-squared given by:

@@

\begin{equation} \label{equ:chi2corr}
\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{s}^2}
\end{equation}

Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
that this formula encompasses the general two-component case. In the single-MBB
case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
but Equation \ref{equ:chi2corr} still applies.
